Tail Indices and Scale Parameters in Financial Time Series

### 2017-03-31 papers/FX/draft.tex
Added the 20seconds CV.

\input{../../physics_common.tex}

@@

Also of concern is the distribution of the test statistic under the
null hypothesis. This distribution is only known asymptotically (given
in equation \eqref{eq:Q1_distr}) when the sample size tends to
infinity. The rate at which the finite-sample distribution tends to
\eqref{eq:Q1_distr} is unclear. To find out more about this issue, we
draw samples from the Student's t(3) distribution and compare the
empirical distribution of the test statistic $Q_1$ with the
empirical distribution of \eqref{eq:Q1_distr}, which we also obtain by
simulating the Brownian motion $W(t)$.

@@

\bibliographystyle{unsrt}
\bibliography{../../thesis/econophysics}
\end{document}

>>>>

%\input{../../physics_common.tex}
\input{physics_common.tex}

@@

Also of concern is the distribution of the test statistic under the
null hypothesis. This distribution is only known asymptotically (given
in equation \eqref{eq:Q1_distr}) when the sample size tends to
infinity. The rate at which the finite-sample distribution tends to
\eqref{eq:Q1_distr} is unclear. To find out more about this issue, we
draw samples from the Student's t(3) and t(4) distributions and
compare the empirical distribution of the test statistic $Q_1$ with the
empirical distribution of \eqref{eq:Q1_distr}, which we also obtain by
simulating the Brownian motion $W(t)$. The empirical density functions
are shown in figure \ref{fig:Q1_distr}.
\begin{figure}[htb!]
  \centering
  \includegraphics[width=\textwidth]{Hoga_AsymptoticDistribution.pdf}
  \caption{Comparison of the asymptotic distribution with empirical
    distribution of $Q_1$ obtained from Student's t samples. The t
    samples have the same size as the S\&P sectors' data, namely 1304
    observations.}
  \label{fig:Q1_distr}
\end{figure}
As seen in the figure, the asymptotic distribution \eqref{eq:Q1_distr}
assigns significantly more mass to the tail than do the empirical
distributions of size 1304. Table \ref{tab:HogaAsymptotic} lists a few
quantiles of these distributions.
\begin{table}[htb!]
  \centering
  \begin{tabular}{c|c|c|c|c}
    & \multicolumn{4}{c}{Quantiles} \\
    \hline
    Distribution & 80\% & 85\% & 90\% & 95\% \\
    \hline
    Asymptotic & 47.48 & 59.61 & 78.90 & 113.12 \\
    t(3) empirical & 23.30 & 28.27 & 35.04 & 46.75 \\
    t(4) empirical & 25.76 & 31.13 & 38.81 & 56.32
  \end{tabular}
  \caption{Quantiles of the asymptotic and empirical test statistic
    distributions}
  \label{tab:HogaAsymptotic}
\end{table}

@@

\bibliographystyle{unsrt}
%% \bibliography{../../thesis/econophysics}
\bibliography{econophysics}
\end{document}
